### 2020-06-28 thesis_template/0_Prelim/abs.tex
corrected

Many existing modern cloud-based data processing systems such as Hadoop, Spark or Flink use
Java Virtual Machine (JVM) and taking full advantage of features such as automated memory management in JVM
including Garbage Collection (GC) which may lead to a significant overhead.
Dataflow-based systems like Spark allow programmers to define complex objects in a
host language like Java to manipulate and transfer tremendous amount of data.

@@

System languages like C++ or Rust seems to be a better choice to
develop systems for Big Data processing because they do not relay on JVM.
By using a system language, a developer has full control on the memory management.
% Therefore, one can implement systems with more optimized memory management strategies.
We found Rust programming language to be a good candidate due to its ability to write memory-safe and
fearless concurrent codes with its concept of memory ownership and borrowing.
Rust programming language includes many possible strategies to optimize memory management for Big Data processing including
selection of different variable types, use of Reference Counting, and multithreading with Atomic Reference Counting.

>>>>

Many existing modern cloud-based data processing systems such as Hadoop, Spark or Flink use
Java Virtual Machine (JVM) and take full advantage of features such as automated memory management in JVM
including Garbage Collection (GC) which may lead to a significant overhead.
Dataflow-based systems like Spark allow programmers to define complex objects in a
host language like Java to manipulate and transfer tremendous amount of data.

@@

System languages like C++ or Rust seem to be a better choice to
develop systems for Big Data processing because they do not relay on JVM.
By using a system language, a developer has full control on the memory management.
% Therefore, one can implement systems with more optimized memory management strategies.
We found Rust programming language to be a good candidate due to its ability to write memory-safe and
fearless concurrent codes with its concept of memory ownership and borrowing.
Rust programming language includes many possible strategies to optimize memory management for Big Data processing including
a selection of different variable types, use of Reference Counting, and multithreading with Atomic Reference Counting.

### 2020-06-28 thesis_template/0_Prelim/ack.tex
corrected

Foremost, I would like to show my appreciation to my advisor Prof. Kia Teymourian for his guidance, encouragement and support.
His expertise and insights were essential for this research work. His passion for research and education motivates me and push this thesis to be a precious work for me.

@@

Finally, I would like to express special thanks to my parents to support this excellent educational opportunity.

>>>>

Foremost, I would like to show my appreciation to my advisor Prof. Kia Teymourian for his guidance, encouragement and support.
His expertise and insights were essential for this research work. His passion for research and education motivates me and his experience is instrumental to the completion of the thesis.

@@

Finally, I would like to express special thanks to my parents for supporting this excellent educational opportunity.

### 2020-06-28 thesis_template/1_Intro/intro.tex
corrected

\section{Motivation}
\label{sec:motivation}
Cluster computing tool for Big Data Analysis has been more important as magnitude and quality of data that we can obtain increases. 
Recently, almost all businesses stand on data, from web marketing analysis to factory automations. The leverage of data is ubiquitous, because 
there are many open source tools to analyze data and cloud computer infrastructure which can support computation for massive amount of data. 
The improvement of accessibility to these technologies has democratized data driven businesses by 
eliminating significant amount of initial investment.

However these computation resources do not come for free; we need to pay money to use these resources. Usually, user needs to pay depending on usage of computational resources. 
If your process of data analysis is too long or need to use number of clusters with high speck specification, the cost may end up significantly hight.
To address these problems, the quality of analysis tool is critical. If the tool can optimize the runtime performance and usage of computational resources, 
the cost for running the businesses can become efficient.

@@

These tools are constructed on top of Java Virtual Machine (JVM). JVM abstracts hardware and memory management from the developer so that the development is fairly easy. 
In addition, Java or Scala compiled code is platform-independent, which can run on any machine with JVM. However, these advantages may be really critical weakness when it comes to 
processing big data. JVM abstract away most detail regarding memory management from the system designer, including memory deallocation, reuse, and movement, as well as pointers, 
object serialization and deserialization. Since managing and utilizing memory is one of the most important factors determining Big Data systems' performance, 
reliance on a managed environment can mean an order-of-magnitude increase in CPU cost for some computations. This cost may be unacceptable for high-performance tool development by an expert.

To overcome these problems, one can use programming languages with more control on hardware, system languages, for development of Big Data tools. For example, C++ is a general-purpose, statically typed, 
compiled programming language which supports multiple programming paradigm. It is also a system language which gives full control over hardware. 
There are several researches or projects \cite{DBLP:conf/sigmod/0001BLLMSTYJ18} where developers and 
researchers implement Big Data tools with this language. These tools shows significantly better performances than those developed with application languages. 
Although the evidence of the advantage of building high speed computational tools with C++ has been discovered, the steep learning curve and difficulty of writing memory safe codes are barrier to technology diffusion.

@@

Even though Rust can be a great candidate to develop Big Data processing tools, there are few study for development on such tools with Rust programming.

@@

In addition, Reference Counting takes important role in Rust ownership concept. By using Reference Counting, a value is able to have multiple owners.
This situation may happen quite often, when we want to acquire complex values from contiguous memory regions. 
Reference Counting has both advantage and disadvantage. 
Reference count can share data which might decrease unnecessary copy of data, but checking reference count might be a overhead.

Atomic Reference Counting is ubiquitous in Rust multithreading program. Atomic Reference Count also has similar features to Reference Counting. 
In addition, it is allowed to use among different threads. This may lead additional overhead from atomic operation.

>>>>

\section{Motivation}
\label{sec:motivation}
Cluster computing tools for Big Data Analysis have been more important as magnitude and quality of data that we can obtain increases. 
Recently, almost all businesses stand on data, from web marketing analysis to factory automations. The leverage of data is ubiquitous, because 
there are many open source tools to analyze data and cloud computer infrastructure which can support computation for massive amount of data. 
The improvement of accessibility to these technologies has democratized data driven businesses by 
eliminating significant amount of initial investment.

However these computation resources do not come for free; we need to pay money to use these resources. Usually, users need to pay depending on usage of computational resources. 
If your process of data analysis is too long or needs to use number of clusters with high speck specification, the cost may end up significantly hight.
To address these problems, the quality of analysis tool is critical. If the tool can optimize the runtime performance and usage of computational resources, 
the cost for running the businesses can become efficient.

@@

These tools are constructed on top of Java Virtual Machine (JVM). JVM abstracts hardware and memory management from the developer so that the development is fairly easy. 
In addition, Java or Scala compiled code is platform-independent, which can run on any machine with JVM. However, these advantages may be really critical weaknesses when it comes to 
processing big data. JVM abstract away most detail regarding memory management from the system designer, including memory deallocation, reuse, and movement, as well as pointers, 
object serialization and deserialization. Since managing and utilizing memory is one of the most important factors determining Big Data systems' performance, 
reliance on a managed environment can mean an order-of-magnitude increase in CPU cost for some computations. This cost may be unacceptable for a high-performance tool development by an expert.

To overcome these problems, one can use programming languages with more control on hardware, system languages, for development of Big Data tools. For example, C++ is a general-purpose, statically typed, 
compiled programming language which supports multiple programming paradigm. It is also a system language which gives full control over hardware. 
There are several researches or projects \cite{DBLP:conf/sigmod/0001BLLMSTYJ18} where developers and 
researchers implement Big Data tools with this language. These tools shows significantly better performances than those developed with application languages. 
Although the evidence of the advantage of building high speed computational tools with C++ has been discovered, the steep learning curve and difficulty of writing memory safe codes are barriers to technology diffusion.

@@

Even though Rust can be a great candidate to develop Big Data processing tools, there are few studies for development on such tools with Rust programming.

@@

In addition, Reference Counting takes an important role in Rust ownership concept. By using Reference Counting, a value is able to have multiple owners.
This situation may happen quite often, when we want to acquire complex values from contiguous memory regions. 
Reference Counting has both advantage and disadvantage. 
Reference count can share data which might decrease unnecessary copy of data, but checking reference count might be a overhead.

Atomic Reference Counting is ubiquitous in Rust multithreading program. Atomic Reference Count also has similar features to Reference Counting. 
In addition, it can be used among different threads. This may lead additional overhead from atomic operation.

### 2020-06-28 thesis_template/2_RelatedWork/model/application_to_system_language.tex
need object size and conclusion documentation
corrected

Considered overhead produced by Memory Management in JVM, use of system language for development of Big Data tool can be one of solutions rather than application language, such as Java and Scala. 
System languages, such as C and C++, are languages that give developer total control over the hardware and de/allocation of memory without GC. 
These features enable program written in system languages to optimized performance taking full advantage of hardware.

To take example, one can build Big Data tool with C++. C++ is one of the most popular system languages which has Object-oriented features. 
C++ has functions which provide control over memory to developers. In another word, it is responsibility for one to manage memory properly and safely. 
The functions, malloc() and free(), take roll for memory allocation and deallocation in respectively. The manual memory de/allocation may cause several problems and require developers 
attention to the problems with significant effort for debugging and testing. Here, we explain two of the most common problems regarding to memory management in existing system languages.

Dangling pointer or reference is a pointer or reference pointing to object that no longer exists. The situation of dangling pointer happens 
because of deallocation of memory without modification of value of the pointer. 
If the memory region is reallocated for other object and the dangling pointer tries to access the original object, the unpredictable behavior may result.

Memory leak occurs when memory is allocated and no longer referenced so that the object in the memory location cannot be reached and released.
This is result of dereferencing object without deallocation. Memory leak consumes more memory than necessary by making unreachable location.

Some solutions are established to address these problems. Actually GC is a high-level solution that guarantees memory safety. 
C++ has a different solution called Resource Acquisition is Initialization (RAII). In RAII, objects can live within the scope where they are created. 
The memory is released when the object goes out of scope. This solution is more predictable and deterministic than GC. 
However, it is problematic When we need the object out of the scope, returning a value from a function. 
There are several ways to go around this problems, such as smart pointers, copy constructors, and move semantics. 
Nevertheless, these non-orthogonal concepts makes code in disorganize and leads to error prone implementation.

>>>>

Considering the overhead produced by Memory Management in JVM, use of system language for development of Big Data tools can be a better solution rather than application languages, such as Java and Scala. 
System languages, such as C and C++, are languages that give developers total control over the hardware and de/allocation of memory without GC. 
These features enable programs written in system languages to optimize performance taking full advantage of hardware.

For example, one can build Big Data tools with C++. C++ is one of the most popular system languages which has Object-oriented features. 
C++ has functions which provide control over memory to developers. In another words, it is responsible for managing memory properly and safely. 
The functions, malloc() and free(), take roll for memory allocation and deallocation in respectively. The manual memory de/allocation may cause several problems and require developers 
attention to the problems with significant effort for debugging and testing. Here, we explain two of the most common problems regarding memory management in existing system languages.

Dangling pointer or reference is a pointer or reference pointing to object that no longer exists. The situation of dangling pointer happens 
because of deallocation of memory without modification of value of the pointer. 
If the memory region is reallocated for other objects and the dangling pointer tries to access the original object, the unpredictable behavior may result.

Memory leaks occur when memory is allocated and no longer referenced so that the object in the memory location cannot be reached and released.
This is result of dereferencing object without deallocation. Memory leaks consume more memory than necessary by making unreachable location.

Some solutions are established to address these problems. Actually, GC is a high-level solution that guarantees memory safety. 
C++ has a different solution called Resource Acquisition is Initialization (RAII). In RAII, objects can live within the scope where they are created. 
The memory is released when the object goes out of scope. This solution is more predictable and deterministic than GC. 
However, it is problematic when we need the object out of the scope, returning a value from a function. 
There are several ways to go around this problems, such as smart pointers, copy constructors, and move semantics. 
Nevertheless, these non-orthogonal concepts may disorganize code and lead to error prone implementation.

### 2020-06-28 thesis_template/2_RelatedWork/model/gctuning.tex
corrected

There are many different ways that one can improve the performance of GC in Java. One of these is for example avoiding pointer-based data structures, such as HashMap and LinkedList. 
These objects have a "wrapper" object for each entry so that number of object tends to be larger than when when an array is used.

Caching serialized object in memory also reduce number of object and memory usage since the set of objects become a byte or binary array. 
Spark SQL applications use DataFrames\cite{DBLP:conf/sigmod/ArmbrustXLHLBMK15}, 
whose intermediate data are managed by an optimized memory manager named Tungsten.
Tungsten stores the intermediate data in a serialized binary form and performs aggregation functions directly on he serialized objects.
Therefore, the number of Java objects in memory is reduced and it reduces the DC frequency and object marking/sweeping.

>>>>

There are many different ways that one can improve the performance of GC in Java. One of these is for example avoiding pointer-based data structures, such as HashMap and LinkedList. 
These objects have a "wrapper" object for each entry so that number of objects tends to be larger than when when an array is used.

Caching serialized objects in memory also reduces the number of objects and memory usage since the set of objects become a byte or binary array. 
Spark SQL applications use DataFrames\cite{DBLP:conf/sigmod/ArmbrustXLHLBMK15}, 
whose intermediate data are managed by an optimized memory manager named Tungsten.
Tungsten stores the intermediate data in a serialized binary form and performs aggregation functions directly on he serialized objects.
Therefore, the number of Java objects in memory is reduced and it reduces the DC frequency and object marking/sweeping.

### 2020-06-28 thesis_template/2_RelatedWork/model/hadoop_to_spark.tex
corrected

In several Big Data mining tools that have been developed, the most notable ones are MapReduce and Spark. MapReduce is a cluster computing framework 
which supports locality-aware scheduling, fault tolerance, and load balancing. Spark is designed to improve performance for iterative jobs keeping features of MapReduce.

@@

Iterative job is especially common in Machine Learning Algorithm, such as learning a data model using Gradient Descent. In traditional MapReduce framework, each iteration can be expressed as single MapReduce job 
so that each job must reload the data from disk. This leads I/O overhead and deteriorates performance of iterative algorithms.

Interactive analysis is also an inevitable task in modern data science. A data scientist wants tp perform exploratory analysis in interactive way. 
Nevertheless, MapReduce is designed in the way more stable for ad-hoc query, so each analysis can be single MapReduce job. 
To perform multiple analysis to explore dataset, the data needs to be written to and reload from disk many times.

@@

Some of the notable improvements are shown here\cite{DBLP:journals/pvldb/ShiQMJWRO15}. For aggregation operation, map output selectivity, which is the ration of the map output size to the job input size, 
can be significantly reduced by using Spark. Spark uses a map side combiner, hash-based aggregation which is more efficient than sort-based aggregation used in MapReduce. 
For iterative operation, caching the input as Resilient Distributed Datasets (RDDs) can reduce CRU and disk I/O overheads for sequence iteration. 
This RDD caching takes a significant role to improve iterative job, because it is more efficient than other low-level caching approaches such as OS buffer caches, and HDFS caching. 
These caching strategy reduces disk I/O overhead, but CPU overhead, such as parsing text to objects.

>>>>

Among Big Data mining tools that have been developed, the most notable ones are MapReduce and Spark. MapReduce is a cluster computing framework 
which supports locality-aware scheduling, fault tolerance, and load balancing. Spark is designed to improve performance for iterative jobs keeping features of MapReduce.

@@

Iterative job is especially common in Machine Learning algorithms, such as learning a data model using Gradient Descent. In traditional MapReduce framework, each iteration can be expressed as single MapReduce job 
so that each job must reload the data from disk. This leads I/O overhead and deteriorates performance of iterative algorithms.

Interactive analysis is also an inevitable task in modern data science. A data scientist wants to perform exploratory analysis in interactive way. 
Nevertheless, MapReduce is designed in a way more stable for ad-hoc queries, so each analysis can be single MapReduce job. 
To perform multiple analyses to explore dataset, the data needs to be written to and reloaded from disk many times.

@@

Some of the notable improvements are shown here\cite{DBLP:journals/pvldb/ShiQMJWRO15}. For aggregation operations, map output selectivity, which is the ration of the map output size to the job input size, 
can be significantly reduced by using Spark. Spark uses a map side combiner, hash-based aggregation which is more efficient than sort-based aggregation used in MapReduce. 
For iterative operations, caching the input as Resilient Distributed Datasets (RDDs) can reduce CRU and disk I/O overheads for sequence iteration. 
This RDD caching takes a significant role to improve iterative job, because it is more efficient than other low-level caching approaches such as OS buffer caches, and HDFS caching. 
These caching strategy reduces disk I/O overhead, but CPU overhead, such as parsing text to objects.

### 2020-06-28 thesis_template/2_RelatedWork/model/intro.tex
corrected

This chapter describes the related work and concepts to our research in this thesis. 
In Section~\ref{sec:os}, some of topics in Operating Systems are described focusing on memory management in operating systems.
Knowledge of operating systems helps us to understand how operating systems handle memory management and 
how other technologies takes advantage of them. Even though this thesis does not focus technologies used for Linear Algebra Computation, 
there are some active researches in technologies in Linear Algebra Computation for Big Data processing. 
It worths to study these concepts explained in Section~\ref{sec:linalg}. 
In Section~\ref{sec:hadoopspark}, major Big Data processing tools and improvement of these tools are introduced. 
Then, Section~\ref{sec:spark} details technologies used for Apache Spark, which is one of the most popular tools for Big Data processing.
In Section~\ref{sec:appsys} and Section~\ref{sec:rustmem}, the advantages of using System Language and Rust for such tools are discussed respectively.
Finally, Section~\ref{sec:llvm} describes how LLVM thrives computer language development.

>>>>

This chapter describes the related work and concepts to our research in this thesis. 
In Section~\ref{sec:os}, some topics in Operating Systems are described focusing on memory management in operating systems.
Knowledge of operating systems helps us to understand how operating systems handle memory management and 
how other technologies takes advantage of them. Even though this thesis does not focus on technologies used for Linear Algebra Computation, 
there are some active researches in technologies in Linear Algebra Computation for Big Data processing. 
It is worth studying these concepts explained in Section~\ref{sec:linalg}. 
In Section~\ref{sec:hadoopspark}, major Big Data processing tools and improvement of these tools are introduced. 
Then, Section~\ref{sec:spark} details technologies used for Apache Spark, which is one of the most popular tools for Big Data processing.
In Section~\ref{sec:appsys} and Section~\ref{sec:rustmem}, the advantages of using System Language and Rust for such tools are discussed respectively.
Finally, Section~\ref{sec:llvm} describes how LLVM thrives computer language development.

### 2020-06-28 thesis_template/2_RelatedWork/model/llvm.tex
corrected

LLVM (Low Level Virtual Machine) is an umbrella project which contains components of compilation of programming language.
Existing compilers have tightly coupled functionalities so that it is not possible to embed them into other applications.
However, the abstract framework of LLVM decouples the functionalities into peaces and the peaces of functionalities can be reused.

In structure of a compiler, there are three main components; frontend, optimizer, and backend. 
In frontend, a developer designs the interface of source programming language in way where it can be optimized by optimizer. 
Then, backend takes optimized code and produce the native machine code. LLVM has a component called LLVM Intermediate Representation (IR), 
which places itself across frontend to optimizer. IR is designed to host mid-level analyses and transformations that you find in optimizer section of a compiler.
High-level language has many common structures and functionalities, so most of all high-level program languages can be represented with IR. 
Once source code is represented with IR, optimizer can easily find pattern and optimize it in faster time. 
IR is useful in terms of frontend. This is because developer of language frontend need to know only how the IR works and use the framework to develop a language.

>>>>

LLVM (Low Level Virtual Machine) \cite{DBLP:conf/cgo/LattnerA04} is an umbrella project which contains components of compilation of programming languages.
Existing compilers have tightly coupled functionalities so that it is not possible to embed them into other applications.
However, the abstract framework of LLVM decouples the functionalities into pieces and the pieces of functionalities can be reused.

In structure of a compiler, there are three main components; frontend, optimizer, and backend. 
In frontend, a developer designs the interface of source programming language in a way where it can be optimized by an optimizer. 
Then, backend takes optimized code and produce the native machine code.

This separation of functionalities gives reusability to parts of the compiler. Establishing new programming language requires new frontend, 
but the existing optimizer and back end can be reused. This speeds up processes of developing new programming languages.

The reusability of compiler leads to support multiple programming languages 
so that broader set of programmers are involved in the development. 
For open source projects like Rust, This ends up larger community of potential contributors to the development.

Since implementation of frontend can be independent on optimizer and backend, 
development of programming languages becomes easy for people without skills required to implement optimizer and backFend.
This thrives new language development.

LLVM has a component called LLVM Intermediate Representation (IR), 
which places itself across frontend to optimizer. IR is designed to host mid-level analyses and transformations that you find in optimizer section of a compiler.
High-level language has many common structures and functionalities, so most of all high-level program languages can be represented with IR. 
Once source code is represented with IR, optimizer can easily find pattern and optimize it in faster time. 
IR is useful in terms of frontend. This is because developer of language frontend need to know only how the IR works and use the framework to develop a language.

Thanks to emerging of LLVM, many new programming languages and compilers have been developed. Rust compiler is also developed based on LLVM.

### 2020-06-28 thesis_template/2_RelatedWork/model/os.tex
corrected

\subsection{Memory and Process in Operating Systems}
\label{sec:os_mem_process}
A process is a subsection of computation job. A process can work on a CPU core, we can divide process as well.
Basically, each process does not share their memory. However, for multiprocessing, we could avoid this restriction.
Processes can be represented as tree structure, because a process may create other child processes.
Process has 4 states, new, running, waiting, and ready. 
Process is represented in process control block (PCB) with state type, process ID, registers, and so on.
The scheduling for process assigning to CPU core is implemented in queues containing PCB. There are two main queues in this scheduler: 
ready queue and wait queue. The head of process in ready queue is selected for execution and once the process requested I/O request or 
production of child process, the running process will be stored n wait queue. Once the request that the process waiting for end, 
the waiting process will be pushed tail of ready queue.

Processes executing concurrently in the operating system may be either independent processes or cooperating processes executing in the system.
A process is independent if it does not share data with any other processes. A process cooperating if it can affect or be affected by the 
other processed executing in the system. In cooperating process, there are two kinds, shared memory and message passing. 
In shared memory, it removes restriction of not interfering memory region. Message passing can be useful for distribution systems as well.

For a pair of processes to communicate through message, a socket is needed to be established. 
A socket is identified by an IP address concatenated with a port number. When two process communicate, each process will have socket. 
If another process of the same machine wants to communicate, we need new socket to be established. The protocol used in the socket connection
can be TPC and UDP.

\subsection{Multi-threading and Parallelism}
\label{sec:os_thread}
A thread is a basic unit of CPU utilization, so that a process can have multiple thread. Threads share mainly code and data. 
Multi-threading is increasingly popular as the multicore programming becomes in common, because we can run multiple thread on different core.
Creating thread is much cheaper than creating process and it shares resources so that we do not need additional methods to allow threads to 
communicate each other, such as sharing memory and message passing.

@@

Usually a program resides on a disk as binary executable file. To run, the program must be brought into memory and placed within the context of a process.
The process is bound to corresponding parts of the physical memory. Binding program to memory address is staging process. 
There three stages: compile time, load time execution time. The source program is compiled by compiler producing object file. 
After the compilation, the object file is linked with other object file by linker creating executable file . 
Finally, the executable file will be loaded to run execute. At this run time dynamic library link can be done.

If where the process will reside in memory at compile time, absolute code is generated. If this is unknown at the time, 
the binding will be done at load time. At this time, the compiler must generate relocatable code. Otherwise, the binding will be done at 
execution time.

@@

The first part of process of demand paging would be that we check an internal table to check whether the reference is valid or invalid.
If the reference is valid, the process reads the content from the memory. Otherwise, we terminates the process and find the free frame in 
physical memory. Then, we schedule a secondary storage operation to read the desired page into newly allocated frame. 
When the storage complete reading the page, we modify the internal table to indicate the page is now in memory. 
Finally, we restart the instruction that was interrupted.

However, there would be a case where the memory does not have any free frame. In this case, a victim frame that will be replaced with new coming frame should be selected. 
To perform this selection efficiently, a modify bit is tracked for each frame or page. The modify bit represents whether the page is modified since it is loaded from secondary storage. 
If the page or frame is modified, when we swap page we need to update the content in the secondary storage. However, it is not modified, we can simply delete the frame and replace with new frame.

>>>>

\subsection{Memory and Process in Operating Systems}
\label{sec:os_mem_process}
A process is a subsection of computation job. A process can work on a CPU core, we can divide process as well.
Basically, each process does not share their memory. However, for multiprocessing, we could avoid this restriction.
Processes can be represented as tree structures, because a process may create other child processes.
Processes have 4 states, new, running, waiting, and ready. 
Processes are represented in process control block (PCB) with state type, process ID, registers, and so on.
The scheduling for processes assigning to CPU core is implemented in queues containing PCB. There are two main queues in this scheduler: 
ready queue and wait queue. The head of process in ready queue is selected for execution and once the process requested I/O request or 
production of child process, the running process will be stored n wait queue. Once the request that the process is waiting for its end, 
the waiting process will be pushed tail of ready queue.

Processes executing concurrently in the operating system may be either independent processes or cooperating processes executing in the system.
A process is independent if it does not share data with any other processes. A process is cooperating if it can affect or be affected by the 
other processed executing in the system. In cooperating processes, there are two kinds, shared memory and message passing. 
In shared memory, it removes restriction of not interfering memory region. Message passing can be useful for distribution systems as well.

For a pair of processes to communicate through message, a socket is needed to be established. 
A socket is identified by an IP address concatenated with a port number. When two process communicate, each process will have socket. 
If another process of the same machine wants to communicate, we need a new socket to be established. The protocol used in the socket connection
can be TPC and UDP.

\subsection{Multi-threading and Parallelism}
\label{sec:os_thread}
A thread is a basic unit of CPU utilization, so that a process can have multiple thread. Threads share mainly code and data. 
Multi-threading is increasingly popular as the multicore programming becomes in common, because we can run multiple thread on different core.
Creating threads is much cheaper than creating processes and it shares resources so that we do not need additional methods to allow threads to 
communicate each other, such as sharing memory and message passing.

@@

Usually, a program resides on a disk as binary executable file. To run, the program must be brought into memory and placed within the context of a process.
The process is bound to corresponding parts of the physical memory. Starting processes binds programs to the memory address. 
There three stages: compile time, load time execution time. The source program is compiled by compiler producing object file. 
After the compilation, the object file is linked with other object file by linker creating executable file . 
Finally, the executable file will be loaded to run execute. At this run time dynamic library link can be done.

If the process will reside in memory at compile time, absolute code is generated. If this is unknown at the time, 
the binding will be done at load time. At this time, the compiler must generate relocatable code. Otherwise, the binding will be done at 
execution time.

@@

The first part of process of demand paging would be that we check an internal table to check whether the reference is valid or invalid.
If the reference is valid, the process reads the content from the memory. Otherwise, we terminate the process and find the free frame in 
physical memory. Then, we schedule a secondary storage operation to read the desired page into newly allocated frame. 
When the storage finished reading the page, we modify the internal table to indicate that the page is now in memory. 
Finally, we restart the instruction that was interrupted.

However, there could be a case where the memory does not have any free frame. In this case, a victim frame that will be replaced with new coming frame should be selected. 
To perform this selection efficiently, a modify bit is tracked for each frame or page. The modify bit represents whether the page is modified since it is loaded from secondary storage. 
If the page or frame is modified, when we swap page we need to update the content in the secondary storage. However, if it is not modified, we can simply delete the frame and replace it with new frame.

### 2020-06-28 thesis_template/2_RelatedWork/model/rust_memory_management.tex
need object size and conclusion documentation
corrected

\subsection{Move}
In Rust, for most types operations like assigning a value to a variable, passing it to a function, or returning it from a function do not copy the value: they move it. 
With move, a value can be transferred from one owner to another. The previous variable does not have ownership of the value; it is moved to a newly assigned variable. 
To understand how this assignment implementation is unique from other programing languages, Java, C++, and Rust code example of assigning list or vector of strings are shown.

>>>>

\subsection{Move}
In Rust, for most types of operations like assigning a value to a variable, passing it to a function, or returning it from a function does not copy the value: it moves it. 
With each move, a value can be transferred from one owner to another. The previous variable does not have ownership of the value; it is moved to a newly assigned variable. 
To understand how this assignment implementation is unique from other programing languages, Java, C++, and Rust code example of assigning list or vector of strings are shown.

### 2020-06-28 thesis_template/2_RelatedWork/model/spark.tex
corrected

A RDD is essentially a multi-layer Java data structure. A top RDD object references Java array, which intern, references a set of tuple objects. 
The coarse-grained transformations and immutability requires a RDD to be deep-copied to produce a new RDD, but efficiently offers fault tolerance. 
The lost partitions of a RDD can be recomputed in parallel on different nodes rather than rolling back the whole program.

Spark-pipeline consists of sequence of transformations and actions over RDDs. A transformation produces a new RDD from a set of existing RDD. 
An action is method that computes statistics from an RDD. Due to lazy-evaluation nature, transformations do not materialize the newly created RDD. 
Instead, RDD Lineages are created. Lineage is a graph among parent and child RDDs which represents logical execution plan. 
This enhance fault-tolerance and improve ability to optimize execution plan.

@@

All data of these types on JVM heap is managed by JVM GC. GC check references graph of objects, mark whether the objects are used and deallocate memory space occupied by unused objects. 
There are three popular GCs: Parallel, CMS and G1. All of these method track generation of object based on the region of memory. 
The Java logical heap structure is shown in Figure~\ref{fig:javaheap}. As the figure shows, Java logical heap can be separated into three main parts where store objects for each corresponding generation: 
permanent generation, young generation, and old generation. The region for permanent generation stores metadata required by JVM to describe 
class and method used in application which will be permanently lived on the region of memory. The overview of Java GC is shown in Figure~\ref{fig:javagc}. 
The outer box represents region for particular generation. The inner box and the number represents object and its age in GC.

@@

Because of the problem of STW and copying objects to different physical memory pages , JVM GC cause huge overhead when number of objects is large. 
Therefore, GC become severe issue in Big Data processing where might produce significant number of object.

>>>>

A RDD is essentially a multi-layer Java data structure. A top RDD object references Java array, which in tern, references a set of tuple objects. 
The coarse-grained transformations and immutability requires a RDD to be deep-copied to produce a new RDD, but efficiently offers fault tolerance. 
The lost partitions of a RDD can be recomputed in parallel on different nodes rather than rolling back the whole program.

Spark-pipeline consists of sequence of transformations and actions over RDDs. A transformation produces a new RDD from a set of existing RDD. 
An action is a method that computes statistics from an RDD. Due to lazy-evaluation nature, transformations do not materialize the newly created RDD. 
Instead, RDD Lineages are created. Lineage is a graph among parent and child RDDs which represents logical execution plan. 
This enhance fault-tolerance and improve ability to optimize execution plan.

@@

All data of these types on JVM heap is managed by JVM GC. GC check reference graphs of objects, mark whether the objects are used and deallocate memory space occupied by unused objects. 
There are three popular GCs: Parallel, CMS and G1. All of these methods track generation of objects based on the region of memory. 
The Java logical heap structure is shown in Figure~\ref{fig:javaheap}. As the figure shows, Java logical heap can be separated into three main parts where store objects for each corresponding generation: 
permanent generation, young generation, and old generation. The region for permanent generation stores metadata required by JVM to describe 
class and method used in application which will be permanently lived on the region of memory. The overview of Java GC is shown in Figure~\ref{fig:javagc}. 
The outer box represents region for particular generation. The inner box and the number represents object and its age in GC.

@@

Because of the problem of STW and copying objects to different physical memory pages , JVM GC cause huge overhead when number of objects is large. 
Therefore, GC becomes a severe issue in Big Data processing where it might produce significant number of object.

### 2020-06-28 thesis_template/2_RelatedWork/model/summary.tex
corrected

In this chapter, we cover some of main concepts to understand our research. 
The topics of Operating Systems and Linear Algebra Computation are not directly relevant to our research, 
but it is worth to cover these topics for deep analysis of experimental result. 
The advantage and disadvantage of modern Big Data processing tools are discussed and 
some of solutions are introduced. Finally, how Rust can be a good candidate for development of Big Data processing tools and 
details of its technologies are described. In next chapter, we discuss main concepts needed to understand theoretical assumption of our experiments.

>>>>

In this chapter, we cover some of main concepts to understand our research. 
The topics of Operating Systems and Linear Algebra Computation are not directly relevant to our research, 
but it is worth covering these topics for deep analysis of experimental result. 
The advantage and disadvantage of modern Big Data processing tools are discussed and 
some solutions are introduced. Finally, how Rust can be a good candidate for development of Big Data processing tools and 
details of its technologies are described. In the next chapter, we discuss main concepts needed to understand theoretical assumptions of our experiments.
